---
title: "Title of your portfolio"
subtitle: "Portfolio 6 - 161.307 Reproducible Visualisation for Statistics"
author: "Your name goes here"
date: "19 August 2026"
date-format: "D MMM YYYY"
lang: en-GB
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    number-sections: false
    number-offset: -1
    theme: cosmo
    highlight-style: github
    code-fold: false
    self-contained: true
execute:
  echo: true
  warning: false
  message: false
---

Feel free to modify the structure of the template document, as you see fit.

Remember to read the instructions in the question file provided on Stream.
  
## Part A: encoding the same uncertainty two ways

```{r}
# Two different uncertainty encodings chunk
```

## Part B: reading a Bayesian plot
```{r, echo = T}
#| fig-align: center
#| fig-width: 7
library(ggdist)
library(ggplot2)

# Worked example: Beta(2,2) prior updated with 7 successes out of 10 trials
# The posterior is a Beta(2 + 7, 2 + 3) = Beta(9, 5) distribution. 
# This is provided for you, no modelling required.
set.seed(2026)
posterior_draws <- rbeta(10000, 9, 5)

data.frame(value = posterior_draws) |>
  ggplot(aes(x = value)) +
  stat_dotsinterval(quantiles = 50, fill = "darkorange",
                     point_interval = "mean_qi") +
  scale_y_continuous(NULL, breaks = NULL) +
  labs(title = "Posterior distribution of a shooter success rates",
       subtitle = "50 dots, each an equally-likely draw from the posterior",
       x = "Free-thrown success rate") +
  theme_minimal()
```

## Written commentary

### What each of my Part A encoding communicate that the other does not

### Part A plot(s) I would you show to (a) a technical audience familiar with the model, and (b) to a general audience? And why?

### What each dor represents in the quantile-dotplot in Part B comapred to the one of the bootstrap example in the lecture of Week 6

### Interpretation of a credible interval (and difference to a confidence interval)
